PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-02-21 txt/manuscript.tex
Update first example

The PyQBench can be used in two modes: as a Python library and as a CLI script. When used as a
library, PyQBench allows using user--defined discrimination schemes. The user is supposed to provide
a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\phi_0}$,
and unitaries $V_0$ and $V_1$ describing the final measurement. The PyQBench library provides then
the following functionalities.

\begin{enumerate}
	\item Assembling circuits for both postselection and direct sum--based discrimination schemes.
	\item Executing the whole benchmarking scenario on specified hardware.
	\item Interpreting the obtained measurements in terms of discrimination probabilities.
\end{enumerate}
Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt-in for
fine--grained control over the execution of the circuits, For instance, suppose the user wants to
simulate the discrimination experiment on a noisy simulator. In such a case, he or she can define
the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
e.g. to add noise to particular gates, and then run using any Qiskit backend. Finally, the user can
use PyQBench to interpret the measurements to obtain discrimination probability.

The PyQBench library also contains a readily available implementation of all necessary components
needed to run discrimination experiments for parametrized Fourier family of measurements defined in
section \ref{sec:fourier}. However, if one only wishes to use this particular family in benchmarks, then using
PyQBench as a CLI tool might be a simpler choice. When operating as CLI, PyQBench can currently only
run experiments that use parametrized Fourier family, but the whole process is greatly simplified.
Essentially, the CLI tool can be used in two types of workflows:

\begin{itemize}
	\item \emph{synchronous}: in this scenario PyQBench submits circuits to the given device and
	waits for the results.
	\item \emph{asynchronous}: PyQBench submits circuits to the device and then produces
	an intermediate file containing, among others, metadata allowing for querying results later on.
\end{itemize}

The execution of the experiment is driven by configuration files written in YAML \cite{}. Examples
of such files can be found in \ref{sec:examples}, and their detailed description can be found at
PyQBench's documentation website \cite{}.

@@

\subsubsection{Integration with devices and hardware providers}

PyQBench is built around the Qiskit\cite{qiskit} ecosystem. Hence, both the CLI tool and the
\texttt{qbench} library can use any Qiskit--compatible backend. This includes, in particular, IBM Q
backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider}).

When using PyQBench as library, instances of Qiskit backends can be passed to functions that expect
them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
backend. An xample of such file can be found in \ref{sec:examples}, and the detailed description of
the expected format can be found at PyQBench's documentation.

@@

The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
invocation is shown in listing \ref{lst:cli}.
\begin{lstlisting}[caption=Invocation of \texttt{qbench} script, label=lst:cli]
qbench <benchmark-type> <command> <parameters>
\end{lstlisting}
Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
fashion will allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
is \texttt{disc-fourier}.

The \texttt{qbench disc-fourier} command has four subcommands:

\begin{itemize}
	\item \texttt{benchmark}: run benchmarks. This creates either a result YAML file containing
	the measurements or an intermediate YAML file for asynchronous experiments.
	\item \texttt{status}: query status of experiments submitted for given benchmark. This command
	is only valid for asynchronous experiments.
	\item \texttt{resolve}: query the results of asynchronously submitted experiments and write the
	result YAML file. The output of this command is almost identical to the result obtained from
	synchronous experiments.
	\item \texttt{tabulate}: interpret the results of a benchamrk and summarize them in the CSV file.
\end{itemize}

\subsubsection{Asynchronous vs. synchronous execution}
As stated in previous sections, PyQBench CLI can be used in synchronous and asynchronous modes. The
mode of execution is defined in the YAML file describing the backend (see \ref{sec:examples}). We
decided to couple the mode of execution to the backend description because some backends cannot work
in asynchronous mode.

When running \texttt{qbench disc-fourier benchmark}, an intermediate file containing metadata of
submitted experiments is created. This metadata contains, in particular, identifiers of the
submitted jobs. The intermediate file can be used to query the status of the submitted jobs or to
resolve them, i.e. to wait for their completion and get the measurement outcomes.

In synchronous mode, PyQBench first submits all jobs required to run the benchmark, and then
immediately waits for their completion. The advantage of this approach is that no separate
invocation of \texttt{qbench} command is needed to actually download the measurement outcomes. The
downside, however, is that if the script is interrupted while the command is running, the
intermediate results will be lost. This might result, in particular, in financial loss if the
backend used is available as a paid service. Therefore, we recommend using asynchronous mode
whenever possible.

\section{Illustrative examples}

In this section, we present two examples demonstrating the usage of PyQBench. In the first example,
we show how to implement a benchmarking scheme for a user--defined measurement and possible ways of
using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
CLI. We show how to prepare the input files for the experiment and how to run it using the
\texttt{qbench} tool.

\subsection{Using user-defined measurement with \texttt{qbench} library}

\subsection{Using \texttt{qbench} CLI}

In this example, we will use $U = H$ (the Hadamard gate). Since our aim in this section is to
demonstrate the use of PyQBench as a library, we leave out the mathematical details, which can be
found in \ref{app:hadamard}. The explicit formula for discriminator in this example reads:
\begin{equation}
\ket{\psi_0} = \frac{1}{\sqrt{2}} (\ket{00} + \ket{11}),
\end{equation}
with final measurements being equal to
\begin{equation}
V_0 =
\left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
\end{equation}
and \begin{equation}
V_1 =
\left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
\end{equation}
where \begin{equation}
\alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} = \cos\left( \frac{3}{8} \pi \right),
\end{equation}
\begin{equation}
\beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} = \sin\left( \frac{3}{8} \pi \right).
\end{equation}
To use the above benchmarking scheme in PyQBench, we first need to decompose the unitary matrices
above into sequences of gates.
The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
\begin{figure}[h!]
	\centering
	\includegraphics[scale=1.7]{pics/discriminator}
	\caption{Decomposition of the discriminator $\ket{\psi_0}$. }
	\label{fig:discriminator}
\end{figure}
For $V_0$ and $V_1$ observe that $V_0 = \operatorname{RY}\left(\frac{3}{4} \pi \right) $, where $\operatorname{RY}$ is rotation gate around the $Y$ axis defined by
\begin{equation}
\operatorname{RY}(\theta) =
\left(\begin{array}{cc} \cos\frac{\theta}{2} & -\sin\frac{\theta}{2} \\ \sin\frac{\theta}{2} & \cos\frac{\theta}{2} \end{array}\right).
\end{equation}
To obtain $V_1$  we need only to swap the columns, i.e.
\begin{equation}
V_1 = \operatorname{RY}\left(\frac{3}{4} \pi \right) \cdot \operatorname{X}.
\end{equation}
Finally, the optimal probability of correct discrimination is equal to
\begin{equation}
p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{\sqrt{2}}{4}. 
\end{equation}
We will now demonstrate how to implement this theoretical scheme in PyQBench. For this example we
will use the Qiskit Aer simulator \cite{}. First, we import the necessary functions and classes from
PyQBench and Qiskit. We also import \texttt{numpy} for the definition of \texttt{np.pi} constant and
the exponential function. The exact purpose of the imported functions will be described at the point
of their usage.
\begin{lstlisting}[language=Python, caption=Imports needed for running benchmarking example]
import numpy as np
from qiskit import QuantumCircuit, Aer
from qbench.schemes.postselection import benchmark_using_postselection
from qbench.schemes.direct_sum import benchmark_using_direct_sum
\end{lstlisting}
To implement the discrimination scheme in PyQBench, we need to define all the necessary components
as Qiskit instructions. We can do so by constructing a circuit object acting on qubits 0 and 1 and
then converting them using \texttt{to\_instruction()} method.
\begin{lstlisting}[language=Python, caption= Defining components for Hadamard experiment]
def state_prep():
	circuit = QuantumCircuit(2)
	circuit.h(0)
	circuit.cnot(0, 1)
	return circuit.to_instruction()

@@

In the simplest scenario, when one does not want to tweak execution details and simply wishes to run
the experiment on a given backend, everything that is required is now to run
\texttt{benchmark\_using\_postselection} function.

@@

\begin{lstlisting}[language=Python, caption=Simulation benchmark by using direct sum]
direct_sum_result = benchmark_using_direct_sum(
	backend=simulator,
	target=1,
	ancilla=2,
	state_preparation=state_prep(),
	u_dag=u_dag(),
	v0_v1_direct_sum_dag=v0_v1_direct_sum_dag(),
	num_shots_per_measurement=10000,
)
\end{lstlisting}
Finally, we calculate the empirical probability obtained from postselection and direct sum experiment and calculate the absolute error between analytical and empirical results. 
\begin{lstlisting}[language=Python, caption=Computation of discrimination probability]
p_succ = (2 + np.sqrt(2)) / 4
print(f"Analytical p_succ = {p_succ}")
print(
f"Postselection: p_succ = {postselection_result}, abs. error = {p_succ - postselection_result}"
)
print(f"Direct sum: p_succ = {direct_sum_result}, abs. error = {p_succ - direct_sum_result}")

@@

\subsubsection{Gaining more control over the benchmarking process}
In the example presented above we used functions that automate the whole process - from the circuit assembly, through running the simulations to interpreting the results. But what if we want more control over some parts of this process? 
One possibility would be to add some additional parameters to \textit{benchmark\_using\_xyz} functions, but this approach is not scalable. Moreover, there is no way we can anticipate all the possible use cases.
 We decided on another approach.  PyQBench provides functions performing:
\begin{enumerate}
\item assembly of circuits needed for experiment, provided the components discussed above
\item interpretation of the obtained measurements
\end{enumerate}
 The difference between the two approaches is illustrated on the diagrams below.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{pics/scheme1}
%		\caption{$y=x$}
		\label{fig:simplified}
	\end{subfigure}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
	\includegraphics[width=0.8\textwidth]{pics/scheme2}
		\label{fig:execution}
	\end{subfigure}
\end{figure}

@@

By choosing this approach we need to divide the experiment into two parts:
assembling  circuits and running  circuits.

Let us focus only on the postselection case, as the direct sum case is analogous. In addition, we need to import two more functions from PyQBench.
\begin{lstlisting}[language=Python, caption= Assembling circuits]
from qbench.schemes.postselection import (
assemble_postselection_circuits,
compute_probabilities_from_postselection_measurements,
)

@@

\end{lstlisting}
The function \textit{assemble\_postselection\_circuits} creates all of neceserry circuits as a dictionary. Each informs if the circuit implements $U^\dagger$ or $\Id$ on the target qubit, and which of $V_0$ and
$V_1$ is used.

Now we need to run the circuits. We will run a noisy and noiseless simulation of our circuits.

@@

noise_model = noise.NoiseModel()
noise_model.add_readout_error(error, [0])
noise_model.add_readout_error(error, [1])
\end{lstlisting}
Once we have our noise model ready, we can execute our circuits with and without noise. To this end, we will use Qiskit’s execute function. One caveat is that we have to keep track which measurements correspond to which circuit. We do so by fixing an ordering on the keys in \textit{circuits} dictionary.
\begin{lstlisting}[language=Python, caption=Running  circuits]
from qiskit import execute

@@

counts_noisy = (
	execute(all_circuits, backend=simulator, noise_model=noise_model, shots=10000).result().get_counts()
)

counts_noiseless = execute(all_circuits, backend=simulator, shots=10000).result().get_counts()
\end{lstlisting}
Finally, we compute the success probabilities using  \textit{compute\_probabilities\_from\_\\postselection\_measurements} function.

@@

\end{lstlisting}
The success probability is 0.8524401115559386. Whereas if we obtain a readout error, the success probability is equal to 0.5017958400693446. 
As expected, noisy simulations gave us results that are further away from the exact ones.
This concludes introduction to PyQBench library.

\section{PyQBench as a CLI tool}\label{sec:pyqbench-as-cli}
Using PyQBench as a library allows one to conduct arbitrary two-qubit von Neumann measurement experiment. However, as discussed in the previous guide, it requires some amount of boilerplate code.
For a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
The workflow is describe as a list of steps:

>>>>

The PyQBench can be used in two modes: as a Python library and as a CLI script. When used as a
library, PyQBench allows customization of discrimination scheme. The user provides
a unitary matrix $U$ defining the measurement to be discriminated, the discriminator $\ket{\phi_0}$,
and unitaries $V_0$ and $V_1$ describing the final measurement. The PyQBench library provides then
the following functionalities.

\begin{enumerate}
	\item Assembling circuits for both postselection and direct sum--based discrimination schemes.
	\item Executing the whole benchmarking scenario on specified backend (either real hardware or
	software simulator).
	\item Interpreting the obtained outputs in terms of discrimination probabilities.
\end{enumerate}
Note that the execution of circuits by PyQBench is optional. Instead, the user might want to opt-in for
fine--grained control over the execution of the circuits, For instance, suppose the user wants to
simulate the discrimination experiment on a noisy simulator. In such a case, he or she can define
the necessary components and assemble the circuits using PyQBench. The circuits can then be altered,
e.g. to add noise to particular gates, and then run using any Qiskit backend by the user. Finally,
PyQBench can be used to interpret the measurements to obtain discrimination probability.

The PyQBench library also contains a readily available implementation of all necessary components
needed to run discrimination experiments for parametrized Fourier family of measurements, defined
previously in section \ref{sec:fourier}. However, if one only wishes to use this particular family
of measurements in their benchmarks, then using PyQBench as a command line tool might be a simpler
choice. PyQBench's command line interface allows for running the whole benchmarking process without
writing Python code. The configuration of CLI is done by YAML \cite{} files describing the benchmark
to be performed and the description of backend on which the benchmark should be run. Importantly,
the YAML configuration files are reusable. The same benchmark can be used with different backends
and vice versa.

The next section describes important architectural decisions taken when creating PyQBench, and
how they affect the end user experience.

@@

PyQBench can be installed from official Python Package Index (PyPI) by running \texttt{pip install
pyqbench}. In a properly configured Python environment the installation process should also make the
\texttt{qbench} command available to the user without a need for further configuration.

\subsubsection{Integration with hardware providers and software simulators}

PyQBench is built around the Qiskit\cite{qiskit} ecosystem. Hence, both the CLI tool and the
\texttt{qbench} library can use any Qiskit--compatible backend. This includes, IBM Q
backends (available by default in Qiskit) and Amazon Braket devices and simulators (available
through \texttt{qiskit-braket-provider} package \cite{qiskit-braket-provider}).

When using PyQBench as library, instances of Qiskit backends can be passed to functions that expect
them as parameters. However, in CLI mode, the user has to provide a YAML file describing the
backend. An example of such file can be found in \ref{sec:examples}, and the detailed description of
the expected format can be found at PyQBench's documentation.

@@

The Command Line Interface (CLI) of PyQBench has nested structure. The general form of the CLI
invocation is shown in listing \ref{lst:cli}.
\begin{lstlisting}[caption=Invocation of \texttt{qbench} script, label=lst:cli]
qbench <benchmark-type> <command> <parameters>
\end{lstlisting}
Currently, PyQBench's CLI supports only one type of benchmark (discrimination of parametrized
Fourier family of measurements), but we decided on structuring the CLI in a hierarchical
fashion to allow for future extensions. Thus, the only accepted value of \texttt{<benchmark-type>}
is \texttt{disc-fourier}.
%
The \texttt{qbench disc-fourier} command has four subcommands:

\begin{itemize}
	\item \texttt{benchmark}: run benchmarks. This creates either a result YAML file containing
	the measurements or an intermediate YAML file for asynchronous experiments.
	\item \texttt{status}: query status of experiments submitted for given benchmark. This command
	is only valid for asynchronous experiments.
	\item \texttt{resolve}: query the results of asynchronously submitted experiments and write the
	result YAML file. The output of this command is almost identical to the result obtained from
	synchronous experiments.
	\item \texttt{tabulate}: interpret the results of a benchamrk and summarize them in the CSV file.
\end{itemize}
%
We present usage of each of the above commands later in section \ref{sec:examples}.

\subsubsection{Asynchronous vs. synchronous execution}
PyQBench's CLI can be used in synchronous and asynchronous modes. The
mode of execution is defined in the YAML file describing the backend (see section
\ref{sec:examples} for example of this configuratoin). We decided to couple the mode of execution to
the backend description because some backends cannot work in asynchronous mode.

When running \texttt{qbench disc-fourier benchmark} in asynchronous mode, the PyQBench submits all
the circuits needed to perform a benchmark and then wirte an intermediate YAML file
containing metadata of submitted experiments. In particular, this metadata contains information on
how to correlate submitted job identifiers with particular circuits. The intermediate file can be
used to query the status of the submitted jobs or to resolve them, i.e. to wait for their completion
and get the measurement outcomes.

In synchronous mode, PyQBench first submits all jobs required to run the benchmark, and then
immediately waits for their completion. The advantage of this approach is that no separate
invocation of \texttt{qbench} command is needed to actually download the measurement outcomes. The
downside, however, is that if the script is interrupted while the command is running, the
intermediate results will be lost. Therefore, we recommend using asynchronous mode
whenever possible.

\section{Illustrative examples}
\label{sec:examples}
In this section, we present two examples demonstrating the usage of PyQBench. In the first example,
we show how to implement a discrimination scheme for a user--defined measurement and possible ways
of using this scheme with \texttt{qbench} library. The second example demonstrates the usage of the
CLI. We show how to prepare the input files for the benchmark and how to run it using the
\texttt{qbench} tool.

\subsection{Using user-defined measurement with \texttt{qbench} package}
In this example, we will demonstrate how \texttt{qbench} package can be used with user--defined
measurement. For this purpose, we will use $U = H$ (the Hadamard gate). The detailed calculations
that lead to the particular form of the discriminator and final measurements can be found in
\ref{app:hadamard}. 
\noindent
The explicit formula for discriminator in this example reads:
\begin{equation}
\ket{\psi_0} = \frac{1}{\sqrt{2}} (\ket{00} + \ket{11}),
\end{equation}
with final measurements being equal to
\begin{equation}
V_0 =
\left(\begin{array}{cc} \alpha & -\beta\\ \beta & \alpha \end{array}\right),
\end{equation}
and \begin{equation}
V_1 =
\left(\begin{array}{cc} -\beta & \alpha \\ \alpha & \beta \end{array}\right),
\end{equation}
where \begin{equation}
\alpha = \frac{\sqrt{2 - \sqrt{2}}}{2} = \cos\left( \frac{3}{8} \pi \right),
\end{equation}
\begin{equation}
\beta  = \frac{\sqrt{2  + \sqrt{2}}}{2} = \sin\left( \frac{3}{8} \pi \right).
\end{equation}
To use the above benchmarking scheme in PyQBench, we first need to decompose the unitary matrices
above into sequences of gates.
The circuit taking $\ket{00}$ to the Bell state $\ket{\psi_0}$  comprises the Hadamard gate followed by CNOT gate on both qubits (see Fig.~\ref{fig:discriminator}).
\begin{figure}[h!]
	\centering
	\includegraphics[scale=1.7]{pics/discriminator}
	\caption{Decomposition of the discriminator $\ket{\psi_0}$. }
	\label{fig:discriminator}
\end{figure}
For $V_0$ and $V_1$ observe that $V_0 = \operatorname{RY}\left(\frac{3}{4} \pi \right) $, where $\operatorname{RY}$ is rotation gate around the $Y$ axis defined by
\begin{equation}
\operatorname{RY}(\theta) =
\left(\begin{array}{cc} \cos\frac{\theta}{2} & -\sin\frac{\theta}{2} \\ \sin\frac{\theta}{2} & \cos\frac{\theta}{2} \end{array}\right).
\end{equation}
To obtain $V_1$  we need only to swap the columns, i.e.
\begin{equation}
V_1 = \operatorname{RY}\left(\frac{3}{4} \pi \right) \cdot \operatorname{X}.
\end{equation}
Finally, the optimal probability of correct discrimination is equal to
\begin{equation}
p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{\sqrt{2}}{4}. 
\end{equation}
We will now demonstrate how to implement this theoretical scheme in PyQBench. For this example we
will use the Qiskit Aer simulator \cite{}. First, we import the necessary functions and classes from
PyQBench and Qiskit. We also import \texttt{numpy} for the definition of \texttt{np.pi} constant and
the exponential function. The exact purpose of the imported functions will be described at the point
of their usage.
\begin{lstlisting}[language=Python, caption=Imports needed for running benchmarking example]
import numpy as np
from qiskit import QuantumCircuit, Aer
from qbench.schemes.postselection import benchmark_using_postselection
from qbench.schemes.direct_sum import benchmark_using_direct_sum
\end{lstlisting}
To implement the discrimination scheme in PyQBench, we need to define all the necessary components
as Qiskit instructions. We can do so by constructing a circuit object acting on qubits 0 and 1 and
then converting them using \texttt{to\_instruction()} method.
\begin{lstlisting}[language=Python, caption= Defining components for Hadamard experiment]
def state_prep():
	circuit = QuantumCircuit(2)
	circuit.h(0)
	circuit.cnot(0, 1)
	return circuit.to_instruction()

@@

In the simplest scenario, when one does not want to tweak execution details and simply wishes to run
the experiment on a given backend, everything that is required is now to run
\texttt{benchmark\_using\_postselection} or \texttt{benchmark\_using\_direct\_sum} function,
depending on the user preference.

@@

\begin{lstlisting}[language=Python, caption=Simulation benchmark by using direct sum]
direct_sum_result = benchmark_using_direct_sum(
	backend=simulator,
	target=1,
	ancilla=2,
	state_preparation=state_prep(),
	u_dag=u_dag(),
	v0_v1_direct_sum_dag=v0_v1_direct_sum_dag(),
	num_shots_per_measurement=10000,
)
\end{lstlisting}
The \texttt{postselection\_result} and  \texttt{direct\_sum\_result} variables contain now the
empirical probabilities of correct discrimination. We can compare them to the theoretical value and
compute the absolute error.

\begin{lstlisting}[language=Python, caption=Examining the benchmark results]
p_succ = (2 + np.sqrt(2)) / 4
print(f"Analytical p_succ = {p_succ}")
print(
f"Postselection: p_succ = {postselection_result}, abs. error = {p_succ - postselection_result}"
)
print(f"Direct sum: p_succ = {direct_sum_result}, abs. error = {p_succ - direct_sum_result}")
\end{lstlisting}

@@

In the example presented above we used functions that automate the whole process -- from the circuit assembly, through running the simulations to interpreting the results. But what if we want more control over some parts of this process? 
One possibility would be to add some additional parameters to \texttt{benchmark\_using\_xyz}
functions, but this approach is not scalable. Moreover, anticipating all possible uses cases
isimpossible. Therefore, we decided on another approach. PyQBench provides functions performing:
\begin{enumerate}
\item Assembly of circuits needed for experiment, provided the components discussed above.
\item Interpretation of the obtained measurements.
\end{enumerate}
 The difference between the two approaches is illustrated on the diagrams in Fig. \ref{fig:diagrams}.

\begin{figure}[ht!]	
	\centering
	\begin{subfigure}[b]{0.9\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{pics/scheme1}
%		\caption{$y=x$}
		\label{fig:simplified}
	\end{subfigure}
	\vfill
	\begin{subfigure}[b]{0.9\textwidth}
		\centering
	\includegraphics[width=0.8\textwidth]{pics/scheme2}
		\label{fig:execution}
	\end{subfigure}
	\caption{Differences between simplified (top) and user--controlled (bottom) execution of
	benchmarks in PyQBench. Compared to simplified benchmarking, in user--controlled benchmarks the
	user has direct access to the circuits being run, and hence can alter them (e.g. by adding
	noise) and/or choose the parameters used for executing them on the backend.}
	\label{fig:diagrams}
\end{figure}

@@

For the rest of this example, Let us focus only on the postselection case, as the direct sum case is
analogous. We continue by importing two more functions from PyQBench.
\begin{lstlisting}[language=Python, caption= Assembling circuits]
from qbench.schemes.postselection import (
    assemble_postselection_circuits,
    compute_probabilities_from_postselection_measurements,
)

@@

\end{lstlisting}
Recall that for a postselection scheme we have two possible choices of the "unknown" measurement and
two possible choices of a final measurement, which gives a total of four circuits needed to run the
benchmark. The function \texttt{assemble\_postselection\_circuits} creates all four circuits and
places them in a dictionary with keys \texttt{"id\_v0"}, \texttt{"id\_v1"}, \texttt{"u\_v0"},
\texttt{"u\_v1"}.

We will now run our circuits using noisy and noiseless simulation. We start by creating a noise
model using Qiskit.

@@

noise_model = noise.NoiseModel()
noise_model.add_readout_error(error, [0])
noise_model.add_readout_error(error, [1])
\end{lstlisting}
Once we have our noise model ready, we can execute the circuits with and without noise. To this end,
we will use Qiskit’s \texttt{execute} function. One caveat is that we have to keep track which
measurements correspond to which circuit. We do so by fixing an ordering on the keys in the \texttt{circuits} dictionary.
\begin{lstlisting}[language=Python, caption=Running  circuits]
from qiskit import execute

@@

counts_noisy = execute(
	all_circuits, 
	backend=simulator, 
	noise_model=noise_model, 
	shots=10000
).result().get_counts()

counts_noiseless = execute(
	all_circuits, 
	backend=simulator, 
	shots=10000
).result().get_counts()
\end{lstlisting}
Finally, we use the measurement counts to compute discrimination probabilities using \texttt{compute\_probabilities\_from\_postselection\_measurements} function.

@@

\end{lstlisting}
We can now examine the results. We expect that for noisy simulations, the result will be further
away from the target value of \texttt{0.8535533905932737}. For example, in one of our runs we
obtained \texttt{prob\_succ\_noiseless = 0.8524401115559386} and \texttt{prob\_succ\_noisy =
0.5017958400693446}. 
\noindent
This concludes our example. In the next section, we will show how to use PyQBench's CLI.

\subsection{Using \texttt{qbench} CLI} 
Using PyQBench as a library allows one to conduct arbitrary two-qubit von Neumann measurement experiment. However, as discussed in the previous guide, it requires some amount of boilerplate code.
For a Fourier parametrized family of measurements, PyQBench offers a simplified way of performing the experiment using a Command Line Interface (CLI).
The workflow is describe as a list of steps:
